The Astropy Project

### 2017-12-11 main.tex
remove benchmarks table

\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative
accuracy of the conversion from FK4 to Galactic coordinates for all pairs of
tools. This shows, for example, that \astropy, Kapteyn, and PyTPM agree
perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also
agree perfectly amongst themselves. However, there is an offset of around
0.2\arcsec\space with the former three packages. Finally, PyEphem disagrees
with other packages by 0.4--0.8\arcsec. These values are only meant to be
illustrative and will change over time as the benchmarks are refined and the
packages updated.
%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices? Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity. Is the difference between median and mean significant enough to warrant showing both? A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
\begin{table}
\begin{center}
\begin{tabular}{llcccc}
\hline
\hline
Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
          &           & arcsec & arcsec & arcsec & arcsec \\
\hline
astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
kapteyn  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
pytpm    &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
pyast    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
pyslalib &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
\end{table}

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values shown on
    table~\ref{tab:coordinate_benchmarks} of the FK4 to Galactic transformation
    between the different packages. Each comparison block shows four squares
    representing the median, mean, maximum and standard deviation going from
    left to right and bottom to top.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

>>>>

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
This figure shows, for example, that \astropy, Kapteyn, and PyTPM agree
perfectly (light colors, small differences), while PALpy, pySLALIB, and PyAST
also agree perfectly amongst themselves.
However, there is an offset of around 0.2\arcsec\space with the former three
packages.
Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values of the FK4 to Galactic
    transformation between the different packages. Each comparison block shows
    four squares representing the median, mean, maximum and standard deviation
    going from left to right and bottom to top.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}
